### 2023-04-14 README.Rmd
Minor bugfixes and features

The package includes the NGRIP/GICC05 data set 'NGRIP_d18O_and_dust_5cm' downloaded from [Centre for Ice and Climate](https://www.iceandclimate.nbi.ku.dk) at the Niels Bohr Institute of the University of Copenhagen, Denmark, and the table of stadial-interstadial events presented by [Rasmussen et al. (2014)](https://www.sciencedirect.com/science/article/pii/S0277379114003485). Also includes the tie-point presented in [Adolphi et al. (2018)](https://cp.copernicus.org/articles/14/1755/2018/) and [Muscheler et al. (2020)](https://www.cambridge.org/core/journals/radiocarbon/article/testing-and-improving-the-intcal20-calibration-curve-with-independent-records/D72D9214C47FE9441B5E730D33DCCE3D). Other data and tie-points should work as well.

>>>>

The package includes the NGRIP/GICC05 data set 'NGRIP_d18O_and_dust_5cm.xls' downloaded from [Centre for Ice and Climate](https://www.iceandclimate.nbi.ku.dk) at the Niels Bohr Institute of the University of Copenhagen, Denmark, and the table of stadial-interstadial events presented by [Rasmussen et al. (2014)](https://www.sciencedirect.com/science/article/pii/S0277379114003485). Also includes the tie-point presented in [Adolphi et al. (2018)](https://cp.copernicus.org/articles/14/1755/2018/) and [Muscheler et al. (2020)](https://www.cambridge.org/core/journals/radiocarbon/article/testing-and-improving-the-intcal20-calibration-curve-with-independent-records/D72D9214C47FE9441B5E730D33DCCE3D). Other data and tie-points should work as well.
